---
title: "Data_wrangle"
author: "Seung Hyun Sung"
date: "2/6/2022"
output: 
    html_document:
        theme: flatly
        toc: true
        toc_depth: 2
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
    echo = TRUE,
    message = FALSE,
    warning = FALSE)
```

```{r libraries}
library(tidyverse)
library(glue)
```



## Indicate Excluded Rows
  

```{r}
retail_tbl <- read_rds("00_Data/retail_data_tbl.rds")

wrangle_raw_data <- function(data){
    
    create_excel_datetime <- function(x){
    (x * (60 * 60 * 24)) %>% as.POSIXct(origin = "1899-12-30", tz = "GMT")
    }
    
    out_tbl <- data %>% 
        # rename 
        rename(invoice_id = invoice,
           unit_price     = price) %>% 
        mutate(
        invoice_dttm   = create_excel_datetime(invoice_date),
        invoice_date   = as.Date(invoice_dttm),
        stock_code     = stock_code %>% str_to_upper(),
        description    = description %>% str_to_upper(),
        description    = str_replace_all(description, "[^[:alnum:]]", " "),
        cancellation   = str_to_upper(str_detect(invoice_id, "^C"))
        ) %>% 
        select(-sheet_chr) %>% 
        select(customer_id, invoice_id, invoice_date, everything())
    
    return(out_tbl)
}

cleaning_tbl <- retail_tbl %>% wrangle_raw_data()

```

There are number of issues with the dataset. 

__Problems:__
- Stock codes have varying descriptions 
- Stock codes have varying Prices 

Specification 
* Stock code which assigns to M appeals to be short for Manual. Knowing the 'M' is the company's most frequent refund requested item, it must be include for further analysis 
* Damaged goods and unscaleable rows should always be removed from further analysis. 
* Undesired transcational rows inresponsible to customers (financial fees)
  + Flag these rows that wish to exclude from further analysis.
  

__Solutions:__
- use most frequenct description (mode)
- Use median UnitPrice 


## Products Table - Manuals

```{r}
products_tbl <- cleaning_tbl %>% 
    select(stock_code, description, unit_price) %>% 
    distinct() %>% 
    arrange(desc(stock_code)) 

mode <- function(x){
    as.character(x) %>% 
        table() %>% 
        sort(decreasing = TRUE) %>% 
        names() %>% 
        .[1]
}

products_summarised_tbl <- products_tbl %>% 
    filter(!is.na(description)) %>% 
    group_by(stock_code) %>% 
    summarise(
        n = n(),
        median_unit_price = median(unit_price),
        mode_description = mode(description)
    ) %>% 
    ungroup() %>% 
    arrange(desc(n))
```

Remove unneccessary (irrelevant) to transaction products from the product summary table 

```{r}
irrelevant_stock_code_list <- c("POST", "M","D", "DOT", "C2", "PADS", "GIFT", "S", "B", "C3", "CRUK", "adjust")

screen_irrelevant_stock_code_list <- c("ADJUST", "GIFT_0001", "TEST", "BANK", "CHARGE", "AMAZON")

irrelevant_description_list <- c("postage","dotcom postage", "sold as set on dotcom","bank charges", "amazon fee", "amazon", "dotcom", "cruk", "packing charge", "amazon adjustment", "sold as set on dotcom and amazon", "cruk commission", "discount", "samples", "lost")

products_manual_tbl <- products_summarised_tbl %>% 
    filter(!stock_code %>% str_detect(paste(str_to_upper(screen_irrelevant_stock_code_list), collapse = "|"))) %>% 
    filter(!stock_code %in% str_to_upper(irrelevant_stock_code_list)) %>% 
    filter(!mode_description %in% str_to_upper(irrelevant_description_list))

```


# Transaction Data Wranggled 

__Notion__:
- products_manual_tbl: Uniform stock code to description manual data 
- retail_transaction_tbl: Wranggled transaction data (store as backup)
  -- retail_order_tbl: transaction order data without cancellation/refund 

```{r}
retail_transaction_tbl <- cleaning_tbl %>% 
    filter(!stock_code %>% str_detect(paste(str_to_upper(screen_irrelevant_stock_code_list), collapse = "|"))) %>% 
    filter(!stock_code %in% str_to_upper(irrelevant_stock_code_list)) %>% 
    filter(!description %in% str_to_upper(irrelevant_description_list)) %>%
    filter(unit_price > 0) %>% 
    # Add stock price 
    mutate(stock_price = quantity*unit_price)
    
retail_order_tbl <- retail_transaction_tbl %>% 
  filter(cancellation != TRUE)
```

# Save Data 

```{r}
write_rds(products_manual_tbl, "00_Data/data_wranggled/product_data/products_manual_tbl.rds")

write_rds(retail_transaction_tbl, file = "00_Data/data_wranggled/trans_data/retail_transaction_tbl.rds")

write_rds(retail_order_tbl, file = "00_Data/data_wranggled/trans_data/retail_order_tbl.rds")

```


# Holiday Data Wrangle 

```{r}
invoice_country_tbl <- retail_order_tbl %>% 
  distinct(invoice_date, country)

# Load Holiday Data 
holidays_tbl <- read_csv("00_Data/holidays.csv") 
# Load Retrived country list data 
country_abbrv_tbl <- read_rds("00_Data/country_abbrv_tbl.rds")

# Filter Time Span 
min_analyse_date <- min(invoice_country_tbl$invoice_date)
max_analyse_date <- max(invoice_country_tbl$invoice_date)

left_join_tbl <- holidays_tbl %>% 
  filter(ds >= min_analyse_date & ds <= max_analyse_date)

country_holiday_tbl <- invoice_country_tbl %>% 
  distinct(country) %>% 
  left_join(country_abbrv_tbl) %>% 
  left_join(left_join_tbl, by = c("country_abbr" = "country")) %>% 
  filter(complete.cases(.)) 

```

# Save Data 

```{r}
write_rds(country_holiday_tbl, "00_Data/country_holiday_tbl.rds")
```



