---
title: "Data_wrangle"
author: "Seung Hyun Sung"
date: "2/6/2022"
output: 
    html_document:
        theme: flatly
        toc: true
        toc_depth: 2
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
    echo = TRUE,
    message = FALSE,
    warning = FALSE)
```

```{r libraries}
library(tidyverse)
library(glues)
```



## Indicate Excluded Rows
  

```{r}
retail_tbl <- read_rds("00_Data/retail_data_tbl.rds")

wrangle_raw_data <- function(data){
    
    create_excel_datetime <- function(x){
    (x * (60 * 60 * 24)) %>% as.POSIXct(origin = "1899-12-30", tz = "GMT")
    }
    
    out_tbl <- data %>% 
        # rename 
        rename(invoice_id = invoice,
           unit_price     = price) %>% 
        mutate(
        invoice_dttm   = create_excel_datetime(invoice_date),
        invoice_date   = as.Date(invoice_dttm),
        stock_code     = stock_code %>% str_to_upper(),
        description    = str_replace_all(description, "[^[:alnum:]]", " "),
        cancellation   = str_to_upper(str_detect(invoice_id, "^C"))
        ) %>% 
        select(-sheet_chr) %>% 
        select(customer_id, invoice_id, invoice_date, everything())
    
    return(out_tbl)
}

cleaning_tbl <- retail_tbl %>% wrangle_raw_data()

```

There are number of issues with the dataset. 

__Problems:__
- Stock codes have varying descriptions 
- Stock codes have varying Prices 

Specification 
* Stock code which assigns to M appeals to be short for Manual. Knowing the 'M' is the company's most frequent refund requested item, it must be include for further analysis 
* Damaged goods and unscaleable rows should always be removed from further analysis. 
* Undesired transcational rows inresponsible to customers (financial fees)
  + Flag these rows that wish to exclude from further analysis.
  

__Solutions:__
- use most frequenct description (mode)
- Use median UnitPrice 


## Products Table - Manuals

```{r}
products_tbl <- cleaning_tbl %>% 
    select(stock_code, description, unit_price) %>% 
    distinct() %>% 
    arrange(desc(stock_code)) 

mode <- function(x){
    as.character(x) %>% 
        table() %>% 
        sort(decreasing = TRUE) %>% 
        names() %>% 
        .[1]
}

products_summarised_tbl <- products_tbl %>% 
    filter(!is.na(description)) %>% 
    group_by(stock_code) %>% 
    summarise(
        n = n(),
        median_unit_price = median(unit_price),
        mode_description = mode(description)
    ) %>% 
    ungroup() %>% 
    arrange(desc(n))
```



```{r}
screen_stock_code_list <- c("POST", "M","D", "DOT", "C2", "PADS", "GIFT", "S", "B", "C3", "CRUK", "adjust")
screen_description_list <- c("postage","dotcom postage", "sold as set on dotcom","bank charges", "amazon fee", "amazon", "dotcom", "cruk", "packing charge", "amazon adjustment", "sold as set on dotcom and amazon", "cruk commission", "discount", "samples")
    
products_manual_tbl <- products_summarised_tbl %>% 
    filter(!stock_code %>% str_detect("ADJUST|GIFT_0001|TEST|BANK|CHARGE|AMAZON")) %>% 
    filter(!stock_code %in% screen_stock_code_list) %>% 
    filter(!mode_description %in% str_to_upper(screen_description_list))
```


```{r}
cleaned_retail_tbl <- cleaning_tbl %>% 
    select(-description) %>% 
    left_join(products_manual_tbl %>% select(-n), by = "stock_code") %>% 
    rename(description = mode_description) %>% 
    select(customer_id, invoice_date, invoice_id, stock_code, description, median_unit_price, everything()) 

retail_order_tbl <- cleaned_retail_tbl %>% 
    filter(unit_price != 0) %>% 
    filter(cancellation != TRUE)

retail_cancellation_tbl <- cleaned_retail_tbl %>% 
    filter(unit_price != 0) %>% 
    filter(cancellation == TRUE)
```

# Save Data 

- products_manual_tbl: Uniform stock code to description manual data 
- retail_order_tbl: Wranggled transcational data 
- retail_cancellation_tbl: Wranggled cancelled transcation data
- cleaned_retail_tbl: Back-up 

```{r}
write_rds(products_manual_tbl, "00_Data/data_wranggled/product_data/products_manual_tbl.rds")

write_rds(retail_order_tbl, file = "00_Data/data_wranggled/trans_data/retail_order_tbl.rds")

write_rds(retail_cancellation_tbl, file = "00_Data/data_wranggled/trans_data/retail_cancellation_tbl.rds")

write_rds(cleaned_retail_tbl, file = "00_Data/cleaned_retail_tbl.rds")

```
