---
title: "Data Explore I"
author: "Seung Hyun Sung"
date: "1/20/2022"
output:
  html_document:
    code_folding: show
    df_print: paged
    highlight: tango
    number_sections: yes
    theme: flatly
    toc: yes
    toc_depth: 3
  pdf_document:
    toc: yes
    toc_depth: '3'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
    echo = TRUE,
    eval = TRUE,
    message = FALSE,
    warning = FALSE,
    dpi = 300,
    fig.align = "center"
    )
```


```{r libraries}
library(timetk)
library(recipes)
library(DataExplorer)
library(kableExtra)
library(tidyverse)
library(tidytext)
library(readtext)
library(tm)
library(corpus)
library(quanteda)
library(wordcloud)
library(skimr)
library(glue)
library(lubridate)
library(kableExtra)
library(rlang)
library(scales)
library(gridExtra)
library(cowplot)
library(tidyquant)

```


```{r}
retail_tbl <- read_rds("00_Data/retail_data_tbl.rds")

create_excel_datetime <- function(x){
    (x * (60 * 60 * 24)) %>% as.POSIXct(origin = "1899-12-30", tz = "GMT")
}
```

Pull pre-built functions:

* word_clouding_generator
    + generator_description_text_extraction
    + generator_description_word_extraction
    + generator_word_clouding_vector


# Data Moderation 

```{r}
retail_explore_tbl <- retail_tbl %>% 
    rename(invoice_id     = invoice,
           unit_price     = price) %>% 
    mutate(
        row_id = sprintf("ROW%07d", 1:n()),
        .before = 1
    ) %>% 
    mutate(invoice_dttm   = create_excel_datetime(invoice_date),
           invoice_date   = as.Date(invoice_dttm),  
           invoice_month  = format(invoice_dttm, "%B") %>% fct_reorder(invoice_dttm %>% format("%m") %>% as.numeric()),
           invoice_dow    = format(invoice_dttm, "%A") %>% fct_reorder(invoice_dttm %>% format("%m") %>% as.numeric()),
           invoice_dom    = format(invoice_dttm, "%d"),
           invoice_hour   = format(invoice_dttm, "%H"),
           invoice_minute = format(invoice_dttm, "%M"),
           invoice_woy    = format(invoice_dttm, "%V"),
           invoice_ym     = format(invoice_dttm, "%Y%m"),
           invoice_ymts   = ceiling_date(invoice_date, "month")-1,
           stock_code     = stock_code %>% str_to_upper(),
           description    = str_replace_all(description, "[^[:alnum:]]", " "),
           cancellation   = str_to_upper(str_detect(invoice_id, "^C")),
           stock_value   = case_when(unit_price < 0 & quantity < 0 ~ unit_price*abs(quantity),
                                    TRUE ~ unit_price*quantity),
           unidentified_id = case_when(is.na(customer_id) ~ TRUE, 
                                       TRUE ~ FALSE)) %>% 
    group_by(invoice_ym) %>% 
    mutate(invoice_month_prop = as.numeric(invoice_dom)/max(as.numeric(invoice_dom)),
           country = as.factor(country),
           neg_stock_value = ifelse(stock_value >= 0, FALSE, TRUE)) %>% 
    ungroup() 

 
```



# Data Explore

## Missing Customer ID and its multivariable contribution 

Features with missingness: 

* customer_id: 22.7%

* description: 0.41%

Severeness of missing values: 

* customer_id:
    + 0.17% of total income statement unidentified
    
* description:
    + highly unique feature hence its degree of missingness can be negligible 

```{r}
missing_tbl <- retail_explore_tbl %>% 
    map_df(~sum(is.na(.))/length(.)) %>% 
    gather(key = variable, value = missing) %>% 
    mutate(missing_pct = scales::percent(missing)) %>% 
    filter(missing != 0) %>% 
    arrange(desc(missing))

missing_tbl %>% kbl() %>% kable_material()
```


causation: the unit_price feature consists financial statements (a.k.a debt), refunds, discounts, product damage along with the transactional sales.

1.8% of total transcations traced are negative income statement (company's expenses + can be more) and from its stats

* 96% are traceable | individual cost by cases is avg __58$__ 
    + At 100% success, preventing such events ( __0.17%__ of cases) from this group can generate __4.8%__ of company's total revenue 
    
* 4% are not traceable (unidentified id) | individual cost by cases is avg __783$__
    + the corresponding chance are unlikely but its risk are predominantly high
    + At 100% success, preventing such events ( __0.07%__ of cases) can generate __2.6%__ of company's total revenue 


```{r}
summarise_income_unidentified <- function(data, ...){
      data %>% 
        group_by(...) %>% 
        summarise(instances     = n(),
                  total_income  = sum(abs(stock_value))) %>% ungroup() %>% 
        mutate(instances_pct    = instances/sum(instances),
               total_income_pct = total_income/sum(total_income))
}

income_unidentified_tbl <- retail_explore_tbl %>% 
  summarise_income_unidentified(unidentified_id)

income_unidentified_tbl %>% kbl() %>% kable_material()
```

```{r}
instance_n_income_by_tbl <- retail_explore_tbl %>% 
    
    select(unidentified_id, neg_stock_value, stock_value) %>% 
    group_by(unidentified_id, neg_stock_value) %>% 
    summarise(instance    = n(),
              total_income = sum(abs(stock_value))) %>% ungroup() %>% 
    
    mutate(total_instance_pct    = instance/sum(instance),
           total_income_pct      = total_income/sum(total_income),
           avg_income_per_cust = total_income/instance)

instance_n_income_by_tbl %>% kbl() %>% kable_material()           
```


## Univariate Data Explore 

```{r}
retail_skim_list <- partition(skim(retail_explore_tbl))
```

### charater Var 

```{r}
charVar_value_count_tbl <- retail_explore_tbl %>% 
    select(retail_skim_list$character$skim_variable) %>% 
    map_df(~unique(.) %>% length()) %>% 
    gather(
        key = variable, 
        value = level_count
        ) %>% 
    arrange(desc(level_count)) 

charVar_value_count_tbl %>%
    mutate(variable = as_factor(variable) %>% fct_reorder(level_count)) %>% 
    ggplot(aes(variable, level_count)) +
    geom_col(fill = palette_light()[1]) +
    coord_flip() +
    theme_tq()

row_count <- retail_explore_tbl %>% nrow()
```


```{r}
logical_vars <- retail_skim_list$logical$skim_variable %>% sort()

for (plot_varname in logical_vars) {
    cat("--\n")
    cat(glue("{plot_varname}\n"))
    
    na_count <- retail_explore_tbl %>% pull(.data[[plot_varname]]) %>% are_na() %>% sum()
    plot_title <- glue("Barplot of Counts for Variable: {plot_varname} ({na_count} missing values)")
    
    explore_plot <- ggplot(retail_explore_tbl) +
        geom_bar(aes(x = .data[[plot_varname]], fill = .data[[plot_varname]])) +
        xlab(str_to_title(plot_varname)) +
        ylab("Count") +
        scale_y_continuous(labels = label_comma()) +
        ggtitle(plot_title) +
        theme(axis.text.x = element_text(angle = 30, vjust = 0.5)) +
        scale_fill_tq() +
        theme_tq()
    
    plot(explore_plot)
}
```


### Numeric Variable Explore

```{r}
numeric_vars <- retail_skim_list$numeric$skim_variable %>% sort()

for (plot_varname in numeric_vars) {
    cat("--\n")
    cat(glue("{plot_varname}\n"))
    
    plot_var <- retail_explore_tbl %>% pull(.data[[plot_varname]])
    na_count <- plot_var %>% are_na() %>% sum()
    fill = palette_light()[1]
    plot_var %>% summary()  %>% print()
    plot_title <- glue("Histogram Plot for Variable: {plot_varname} ({na_count} missing values)")
    
    all_plot <- ggplot() +
        geom_histogram(aes(x = plot_var, y = ..count..), fill = fill, bins = 30) +
        geom_vline(xintercept = mean(plot_var, na.rm = TRUE),
                   colour = palette_light()[2], size = 1.5) +
        geom_vline(xintercept = median(plot_var, na.rm = TRUE),
                   colour = palette_light()[3], size = 1.5) +
        xlab(str_to_title(plot_varname)) +
        ylab("Count") +
        scale_x_continuous(labels = label_comma()) +
        scale_y_continuous(labels = label_comma()) +
        ggtitle(
            plot_title,
            subtitle = "red line: mean | green line: median"
        ) +
        theme_tq()
    
    pos_data_tbl <- retail_explore_tbl %>%
        filter(.data[[plot_varname]] >= 0) %>%
        mutate(var_val = abs(.data[[plot_varname]]))
    
    pos_log_plot <- ggplot(pos_data_tbl) +
        geom_histogram(aes(x = var_val), fill = fill, bins = 30) +
        xlab(plot_varname) +
        ylab("Count") +
        scale_x_log10(labels = label_comma()) +
        scale_y_continuous(labels = label_comma()) +
        ggtitle("Positive Values") +
        theme_tq()
    
    neg_data_tbl <- retail_explore_tbl %>%
        filter(.data[[plot_varname]] < 0) %>%
        mutate(var_val = abs(.data[[plot_varname]]))
    
    neg_log_plot <- ggplot(neg_data_tbl) +
        geom_histogram(aes(x = var_val), fill = fill, bins = 30) +
        xlab(plot_varname) +
        ylab("Count") +
        scale_x_log10(labels = label_comma()) +
        scale_y_continuous(labels = label_comma()) +
        ggtitle("Negative Values") +
        theme_tq()
    
    plot_grid(
        all_plot,
        NULL,
        pos_log_plot,
        neg_log_plot,
        nrow = 2
    ) %>%
        print()
}

```


### Categorical (factor) Variable Explore

```{r}

factor_vars <- retail_skim_list$factor$skim_variable %>% sort()

for(plot_varname in factor_vars) {
    cat("--\n")
    cat(glue("{plot_varname}\n"))
    
    na_count   <- retail_explore_tbl %>% pull(.data[[plot_varname]]) %>% are_na() %>% sum()
    plot_title <- glue("Barplot of Counts for Factor Variable: {plot_varname} ({na_count} missing values)")
    
    foo <- retail_explore_tbl %>% 
        count(.data[[plot_varname]]) %>% 
        ggplot() +
        geom_bar(aes(x = .data[[plot_varname]], weight = n), fill = palette_light()[1]) +
        xlab(str_to_title(plot_varname)) +
        ylab("Count") +
        scale_x_discrete(labels = ~ abbreviate(.x, minlength = 10)) +
        scale_y_continuous(labels = label_comma()) +
        ggtitle(plot_title) +
        theme(axis.text.x = element_text(angle = 30, vjust = 0.5)) +
        coord_flip() +
        theme_tq()
    
    plot(foo)
    
    desc_plot_tbl <- retail_explore_tbl %>%
        pull(.data[[plot_varname]]) %>%
        fct_lump(n = 20) %>%
        fct_count() %>%
        mutate(f = fct_relabel(f, str_trunc, width = 15))
    
    desc_plot <- ggplot(desc_plot_tbl) +
        geom_bar(aes(x = fct_reorder(f, -n), weight = n), fill = palette_light()[1]) +
        xlab(plot_varname) +
        ylab("Count") +
        scale_x_discrete(labels = abbreviate) +
        scale_y_continuous(labels = label_comma()) +
        ggtitle(plot_title) +
        theme(axis.text.x = element_text(angle = 30, vjust = 0.5)) +
      theme_tq()
    
    desc_plot %>% print()
    
}
```


## Bivariable Data Explore

### Facet Plot: logical variable VS faceted Categorical variable

```{r}

generatorVis_biVar_lgl_fct_factor <- function(data, 
                                              variables = variables,
                                              facet_varname = facet_varname,
                                              dataexp_facet_count_max = 3,
                                              free = NULL){
    
    variables <- logical_vars[!logical_vars %in% facet_varname] %>% sort()
    
    for (plot_varname in variables) {
    cat("--\n")
    cat(plot_varname)
    plot_tbl <- data %>% filter(!are_na(.data[[plot_varname]]))
    
    list <- plot_tbl %>% 
        group_by(.data[[facet_varname]]) %>% 
        count(.data[[plot_varname]], sort = TRUE) %>% ungroup() %>% 
        pull(.data[[facet_varname]]) 
    
    explore_plot <- plot_tbl %>% 
        filter(.data[[facet_varname]] %in% list[which(duplicated(list))]) %>% 
        ggplot() +
        geom_bar(aes(x = .data[[plot_varname]], fill = .data[[plot_varname]])) +
        facet_wrap(facet_varname, scales = free) +
        xlab(str_to_title(plot_varname)) +
        ylab("Count") +
        scale_y_continuous(labels = label_comma()) +
        ggtitle(glue("{facet_varname}-Faceted Histogram for Variable: {plot_varname}")) +
        theme(axis.text.x = element_text(angle = 30, vjust = 0.5)) +
        scale_fill_tq() +
        theme_tq()
    plot(explore_plot)
    }
}
```


```{r}
retail_explore_tbl %>% 
    generatorVis_biVar_lgl_fct_factor(logical_vars, 
                                      facet_varname = "invoice_month")

retail_explore_tbl %>% 
    generatorVis_biVar_lgl_fct_factor(logical_vars, 
                                      facet_varname = "invoice_dow",
                                      free = "free")

retail_explore_tbl %>% 
    generatorVis_biVar_lgl_fct_factor(logical_vars, 
                                      facet_varname = "country",
                                      free = "free")

```


### Continous variable Facet Plot: by Categorical Variables

```{r}

for(facet_varname in factor_vars){
  for(plot_varname in numeric_vars){
  cat("--\n")
  cat(plot_varname)
  
  plot_tbl <- retail_explore_tbl %>% filter(!are_na(.data[[plot_varname]]))
  
  explore_plot <- plot_tbl %>% ggplot() +
    geom_histogram(aes(x = .data[[plot_varname]]), bins = 30, fill = palette_light()[1]) +
    facet_wrap(facet_varname, scales = "free") +
    labs(
      x = plot_varname,
      y = "Count"
    ) +
    scale_x_continuous(labels = label_comma()) +
    scale_y_continuous(labels = label_comma()) +
    ggtitle(glue("{facet_varname}-Faceted Histogram for Variable: {plot_varname}")) +
    theme(axis.text.x = element_text(angle = 30, vjust = 0.5)) +
    theme_tq()
  
  print(explore_plot)
}
}
  
```

### Continous variable Facet Plot: by Logical Variables

```{r}
facet_varname <- c("unidentified_id", "neg_stock_value", "cancellation")
for(plot_varname in numeric_vars){
  cat("--\n")
  cat(plot_varname)
  
  plot_tbl <- retail_explore_tbl %>% filter(!are_na(.data[[plot_varname]]))
  
  explore_plot <- plot_tbl %>% ggplot() +
    geom_histogram(aes(x = .data[[plot_varname]]), bins = 30, fill = palette_light()[1]) +
    facet_wrap(facet_varname, scales = "free") +
    labs(
      x = plot_varname,
      y = "Count"
    ) +
    scale_x_continuous(labels = label_comma()) +
    scale_y_continuous(labels = label_comma()) +
    ggtitle(glue("{facet_varname}-Faceted Histogram for Variable: {plot_varname}")) +
    theme(axis.text.x = element_text(angle = 30, vjust = 0.5)) +
    theme_tq()
  
  print(explore_plot)
}

  
```


### Categorical variable Facet Plot:

```{r}

for(facet_varname in logical_vars){
  for (plot_varname in factor_vars) {
  cat("--\n")
  cat(plot_varname)
  
  plot_tbl <- retail_explore_tbl %>%
    filter(!are_na(.data[[plot_varname]])) 
  
  explore_plot <- ggplot(plot_tbl) +
    geom_bar(aes(x = .data[[plot_varname]], fill = .data[[facet_varname]])) +
    facet_wrap(facet_varname, scales = "free") +
    xlab(plot_varname) +
    ylab("Count") +
    scale_x_discrete(labels = abbreviate) +
    scale_y_continuous(labels = label_comma()) +
    ggtitle(glue("{facet_varname}-Faceted Histogram for Variable: {plot_varname}")) +
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5),
          legend.position = "none") +
    scale_fill_tq() 
  
  plot(explore_plot)
}
}

```


## Explore Aggregate Amount 

The data set is aggregated transaction data hence we will inspect and re-aggregate in various form to explore customer purchasing behaviour. 


### Item counts per transcation 

```{r}
plot_tbl <- retail_explore_tbl %>% 
  filter(quantity > 0) %>% 
  count(invoice_id, name = "n_items") 

plot_tbl %>% 
  ggplot() +
  geom_histogram(aes(x = n_items), bins = 40, fill = palette_light()[1]) +
  scale_x_log10(labels = label_comma()) +
  scale_y_continuous(labels = label_comma()) +
  xlab("Number of Items") +
  ylab("Transaction Count") +
  ggtitle("Histogram of Item Counts per Transactions") +
  theme_tq()
```


### Invoice transation amount 

```{r}
invoice_data_tbl <- retail_explore_tbl %>%
  group_by(invoice_id) %>%
  summarise(
    .groups = "drop",
    invoice_amount = sum(unit_price * quantity) %>% round(2)
  )
  
invoice_mean   <- invoice_data_tbl %>% pull(invoice_amount) %>% mean()   %>% round(2)
invoice_median <- invoice_data_tbl %>% pull(invoice_amount) %>% median() %>% round(2)

ggplot(invoice_data_tbl) +
  geom_histogram(aes(x = invoice_amount), bins = 50) +
  geom_vline(aes(xintercept = invoice_mean),   colour = "black") +
  geom_vline(aes(xintercept = invoice_median), colour = "red") +
  xlab("Invoice Amount") +
  ylab("Count") +
  scale_x_log10(labels = label_comma()) +
  scale_y_continuous(labels = label_comma()) +
  ggtitle(
    label    = "Histogram Plot for Invoice Amount",
    subtitle = glue("Mean is {invoice_mean}, Median is {invoice_median}")
    )
```


### Customer-level amount  

```{r}
customer_data_tbl <- retail_explore_tbl %>%
  group_by(customer_id) %>%
  summarise(
    .groups = "drop",
    customer_spend = sum(unit_price * quantity) %>% round(2)
  )
  
ggplot(customer_data_tbl) +
  geom_histogram(aes(x = customer_spend), bins = 50) +
  xlab("Customer Spend") +
  ylab("Count") +
  scale_x_log10(labels = label_comma()) +
  scale_y_continuous(labels = label_comma()) +
  ggtitle("Histogram Plot for Customer Spend")
```



### Product items with highest cancellation 

```{r}
stock_codes_lookup_tbl <- retail_explore_tbl %>%
  select(stock_code, description) %>%
  distinct() %>%
  arrange(stock_code, description) %>%
  drop_na(description)

stock_code_cancelled_tbl <- retail_explore_tbl %>%
  filter(cancellation == TRUE) %>% 
  mutate(description = str_to_lower(description)) %>% 
  group_by(stock_code, description) %>%
  summarise(count = n(),
            cost  = sum(stock_value)) %>% 
  arrange(desc(count)) %>% ungroup() %>% 
  mutate(cost_text = scales::dollar(cost),
         stock_code = str_glue("_{stock_code}_: {description}({cost_text})"),
         stock_code = as_factor(stock_code) %>% fct_reorder(count)) %>% 
  head(20)

stock_code_cancelled_tbl %>% 
  ggplot(aes(stock_code, count)) +
  geom_col(fill = palette_light()[1]) +
  coord_flip() +
  theme_tq()

```


```{r}
stock_code_summary_tbl <- retail_explore_tbl %>%
  filter(cancellation == FALSE) %>% 
  group_by(stock_code) %>%
  summarise(
    .groups = "drop",
    
    row_count = n(),
    net_quantity = sum(quantity),
    abs_quantity = abs(quantity) %>% sum(),
    net_value    = sum(stock_value),
    abs_value    = abs(quantity) %>% sum()
    ) %>%
  mutate(
    sc_nchar = nchar(stock_code), .before = "row_count"
    )

stock_code_summary_tbl %>% head(20)
```

```{r}
short_stock_codes_tbl <- retail_explore_tbl %>%
  semi_join(stock_code_summary_tbl %>% filter(sc_nchar < 5), by = "stock_code")

short_stock_codes_tbl %>% head(20)
```


## Stock Code Price Data 

```{r}
stock_price_counts_tbl <- retail_explore_tbl %>% 
  group_by(stock_code) %>% 
  summarise(
    .groups     = "drop",
    n_prices    = n(),
    mean_price  = mean(unit_price),
    min_price   = min(unit_price),
    p25_price   = quantile(unit_price)[2],
    p50_price   = quantile(unit_price)[3],
    p75_price   = quantile(unit_price)[4],
    max_price   = max(unit_price),
    range_price = ((max_price - min_price)/ mean_price) %>% round(4)
  ) 

stock_price_counts_tbl %>% head(20)

```


```{r}
stock_distinct_price_counts_tbl <- retail_explore_tbl %>% 
  select(stock_code, unit_price) %>% 
  distinct() %>% 
  group_by(stock_code) %>% 
  summarise(
    .groups     = "drop",
    n_prices    = n(),
    mean_price  = mean(unit_price) %>% round(2),
    min_price   = min(unit_price) %>% round(2),
    p25_price   = quantile(unit_price)[2] %>% round(2),
    p50_price   = quantile(unit_price)[3] %>% round(2),
    p75_price   = quantile(unit_price)[4] %>% round(2),
    max_price   = max(unit_price) %>% round(2),
    range_price = ((max_price - min_price)/ mean_price) %>% round(2)
  ) 

stock_distinct_price_counts_tbl %>% head(20)

stock_distinct_price_counts_tbl %>% arrange(desc(n_prices)) %>% head(20)
```



## Indicate Excluded Rows

There are number of issues with the dataset. 

* Stock code which assigns to M appeals to be short for Manual. Knowing the 'M' is the company's most frequent refund requested item, it must be include for further analysis 

* Damaged goods and unscaleable rows should always be removed from further analysis. 

* Undesired transcational rows inresponsible to customers (financial fees)
  + Flag these rows that wish to exclude from further analysis.

```{r}
"%notin%" <- Negate("%in%")

screen_stock_code <- short_stock_codes_tbl %>% pull(stock_code) %>% unique() 
screen_stock_code_indicator <- c("POST", "D", "DOT", "M", "C2", "PADS", "GIFT", "m", "S", "B", "C3", "CRUK", "ADJUST", "adjust")
# screen_stock_code_indicator <- screen_stock_code[screen_stock_code %notin% c('M', 'm', "D", "S", "CRUK")]

screen_fee_n_commision <- c("postage","dotcom postage", "sold as set on dotcom","bank charges", "amazon fee", "amazon", "dotcom", "cruk", "packing charge", "amazon adjustment", "sold as set on dotcom and amazon", "cruk commission", "discount", "samples")


retail_explore_exclude_tbl <- retail_explore_tbl %>% 
  mutate(
       exclude01_sc_flag = case_when(
          stock_code %in% screen_stock_code_indicator == 1 ~ 1,
          TRUE ~ 0
          ),
        exclude02_damgG_flag = case_when(
          unit_price == 0 ~ 1,
          TRUE ~ 0
          ),
        exclude03_fee_flag = case_when(
          str_to_lower(description) %in% screen_fee_n_commision == 1 ~ 1,
          TRUE ~ 0
          )
       )

include_retail_tbl <- retail_explore_exclude_tbl %>% 
  filter(exclude01_sc_flag == 0) %>%
  filter(exclude02_damgG_flag == 0) %>%
  filter(exclude03_fee_flag == 0) 

```


## Product Items: Stock Code - Abstact Stock Code Manual

### description and stock_code unmatched

```{r}

# Abstract stock code with multiple descriptions 
sc_desc_cleaning_tbl <- include_retail_tbl %>% 
    distinct(description, stock_code) %>%
    
    group_by(stock_code) %>% 
    summarise(
        .groups = "drop",
        description = description,
        count = n()) %>% 
    arrange(desc(count)) %>% 
    
    mutate(unique_flag = ifelse(count == 1, TRUE, FALSE)) 

# Uniform descriptions by second longest naming 
sc_description_match_tbl <- sc_desc_cleaning_tbl %>% 
    filter(unique_flag == FALSE) %>% 
    group_by(stock_code) %>% 
    mutate(nchar = nchar(description)) %>% 
    arrange(stock_code, desc(nchar)) %>% 
    slice(2) %>% ungroup() %>% select(stock_code, description) %>% 
    bind_rows(
        sc_desc_cleaning_tbl %>% 
            filter(unique_flag == TRUE) %>% 
            select(stock_code, description)
        )

# Abstract description with multiple stock_code (reverse)
duplicated_desc_vec <- sc_description_match_tbl %>% 
    group_by(description) %>% 
    count(n_distinct(stock_code)) %>% 
    arrange(desc(n))  %>% 
    filter(n != 1) %>% 
    pull(description)
  
# Slice descriptions with more popular stock_code 
desc_stock_code_match_tbl <- include_retail_tbl %>% 
    mutate(stock_description = str_c(stock_code, description, sep = ":")) %>% 
    group_by(description) %>% 
    count(stock_code, stock_description) %>% ungroup() %>% 
    filter(description %in% duplicated_desc_vec) %>% 
  
    group_by(description) %>% 
    arrange(desc(n)) %>% 
    slice(1) %>% ungroup() %>% 
    select(description, stock_code)

# stock_code - description mannual 
stock_code_description_manual <- sc_description_match_tbl %>% 
  anti_join(desc_stock_code_match_tbl, by = "description") %>% 
  bind_rows(desc_stock_code_match_tbl)
  
# confirm 
length(stock_code_description_manual$stock_code) == length(stock_code_description_manual$description)

```

# Save Data 

- Include & exclude data

- stock_code description manual 

- cleaned data 

```{r}

exclude_retail_tbl <- retail_explore_exclude_tbl %>% 
  filter(row_id %notin% retail_tbl$row_id)


cleaned_retail_tbl <- include_retail_tbl %>% 
  select(-description, -contains("flag"), -sheet_chr) %>% 
  left_join(stock_code_description_manual, by = "stock_code") %>% 
  select(1:stock_code, description, everything())


write_rds(include_retail_tbl, file = "00_Data/include_retail_tbl.rds")
write_rds(exclude_retail_tbl, file = "00_Data/exclude_retail_tbl.rds")

write_rds(stock_code_description_manual, file = "00_Data/data_wranggled/product_data/stock_code_description_manual.rds")
 
write_rds(cleaned_retail_tbl, file = "00_Data/data_wranggled/cleaned_retail_tbl.rds")
```




