---
title: "90 Days Prediction Modelling"
author: "Seung Hyun Sung"
date: "2/11/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# SetUp
-- Engineered Data 
-- Train/Val/Test Data 
-- Functions 

```{r}
train_joined_tbl <- read_rds("00_Data/data_engineered/90_days_prediction/train_joined_tbl.rds")

validation_joined_tbl <- read_rds("00_Data/data_engineered/90_days_prediction/validation_joined_tbl.rds")

test_joined_tbl <- read_rds("00_Data/data_engineered/90_days_prediction/test_joined_tbl.rds")
```


```{r}
modelling_data <- train_joined_tbl

val_data <- validation_joined_tbl
```


## Recipes --

- Model 1: 90-Day Spend Prediction 
```{r}
cust_finanical_feature <- c("frequency", "median_spend", "monetary", "recency", "refund_frequency", "tot_refund_value")

recipe_spend_total <- recipe(spend_90_total ~., data = modelling_data) %>%
    step_rm(spend_90_flag, customer_id, first_pur, 
            max_spend, min_spend) %>% 
    step_dummy(all_nominal()) %>% 
    step_nzv(all_predictors()) %>% 
    step_log(all_of(cust_finanical_feature), 
             spend_90_total, offset = 1) %>% 
    step_range(all_of(cust_finanical_feature), spend_90_total) 

recipe_spend_total %>% prep() %>% juice() %>% glimpse()
```

- Model 2: 90-Day Spend Probability 
```{r}
recipe_spend_probability <- recipe(spend_90_flag ~., data = modelling_data) %>%
    step_rm(spend_90_total, customer_id, first_pur, 
            max_spend, min_spend) %>% 
    step_dummy(all_nominal(), -spend_90_flag) %>% 
    step_nzv(all_predictors()) %>% 
    step_log(all_of(cust_finanical_feature), offset = 1) %>% 
    step_range(all_of(cust_finanical_feature)) 


recipe_spend_probability %>% prep() %>% juice() %>% glimpse()
```


### Models --

- Model 1: 90 Days Spend Prediction 
```{r}
glmnet_spec_1 <- linear_reg(
    penalty = tune(),
    mixture = tune()
    ) %>% 
    set_engine("glmnet")

xgboost_spec_1 <- boost_tree(
    mode = "regression",
    trees = 500,
    learn_rate = tune(),
    min_n      = tune()
    ) %>% 
    set_engine("xgboost")

svm_spec_1 <- svm_rbf(
    mode = "regression",
    cost = tune(),
    rbf_sigma = tune(),
    margin    = tune()
    ) %>% 
    set_engine("kernlab")

linear_spec_1 <- linear_reg(
    mode = "regression",
    engine = "lm",
    penalty = tune(),
    mixture = tune())

RForest_spec_1 <- rand_forest(
    mode   = "regression",
    trees  = 500,
    mtry   = tune(),
    min_n  = tune()
    ) %>% 
    set_engine("randomForest")



```

- Model 1: 90 Days Probability Prediction 
```{r}
xgboost_spec_2 <- boost_tree(
    mode = "classification",
    trees = 500,
    learn_rate = tune(),
    min_n = tune()
    ) %>% 
    set_engine("xgboost")

svm_spec_2 <- svm_rbf(
    mode = "classification",
    cost = tune(),
    rbf_sigma = tune(),
    margin = tune()
    ) %>% 
    set_engine("kernlab")

logistic_spec_2 <- logistic_reg(
    mode = "classification",
    engine = "glm",
    penalty = tune(),
    mixture = tune()
    ) %>% 
    set_engine("glm")
    
RForest_spec_2 <- rand_forest(
    mode = "classification",
    trees = 500,
    mtry = tune(),
    min_n = tune()
    ) %>% 
    set_engine("randomForest")

mlp_spec_2 <- mlp(
    hidden_units = tune(), 
    penalty = tune(), 
    epochs = tune()
    ) %>% 
    set_engine("nnet", trace = 0) %>%
    set_mode("classification")

# crossing(
#   hidden_units = 1:3,
#   penalty = c(0.0, 0.1),
#   epochs = c(100, 200)
# )

```

### Cross Validation 
- Resample 
```{r}

resample <- function(data, .seed = 42, n_fold = 5){
    set.seed(.seed)
    resample_spec <- data %>% 
    vfold_cv(v = n_fold)
    return(resample_spec)
}

resample_spec <- val_data %>% 
    resample(.seed = 42, n_fold = 5)

## -- Model (1): Predict Spend Total
wflwset_setup_spend <- workflow_set(
    preproc = list(
        recipe_spend_total
        ),
    models = list(
        glmnet_spec_1,
        xgboost_spec_1,
        svm_spec_1,
        linear_spec_1,
        RForest_spec_1
    ),
    cross = TRUE
)

## -- Model (2): Predict Spend Probability
wflwset_setup_prob <- workflow_set(
    preproc = list(
        recipe_spend_probability
    ),
    models = list(
        xgboost_spec_2,
        svm_spec_2,
        logistic_spec_2,
        RForest_spec_2,
        mlp_spec_2
    ),
    cross = TRUE
)
```



```{r}
### 3.5 Params Tune Results  
wflwset_tune_result <- wflwset_setup_spend %>% 
    workflow_map(
        fn = "tune_race_anova",
        resamples = resample_spec,
        grid = 15,
        metrics = metric_set(rmse, rsq),
        verbose = TRUE
    )

wflwset_tune_prob_result <- wflwset_setup_prob %>% 
    workflow_map(
        fn = "tune_grid",
        resamples = resample_spec,
        grid = 15,
        metrics = metric_set(accuracy, mse),
        verbose = TRUE
    )
```



- Bloomberg 산업위험 
->>> 자금조달 WACC (weighted average cost of capital): firm's average cost of capital from all sources, including common stock, preferred stock, bonds, and other forms of debt.
- logical 한 계획 및 회계가치 -> 회계법인 -> 가치 평가! 
- DCF 방식 -> 5개월 매출 계획 -> 인권비이다 -> 합리적으로 썼는가? -> discount rate으로 (penalty -> 얼만큼 주어야할까?) --> 
- 1-2 년 후에는 가치가 올라간다! 
- 구체적 계획 -> 누구랑 MOU 했을까? 
- Valuation  평가 



