---
title: "Feature Engineering"
author: "Seung Hyun Sung"
date: "2/12/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# 1. Set Up 
-- Data 
-- Train/Val/Test
-- Functions 
-- Plan 


## Data 
```{r}
trans_invoice_tbl <- read_rds("00_Data/data_wranggled/trans_data/trans_invoice_tbl.rds")

retail_order_tbl <-  read_rds("00_Data/data_wranggled/trans_data/retail_order_tbl.rds")

products_manual_tbl <-  read_rds("00_Data/data_wranggled/product_data/products_manual_tbl.rds")

code_bd_kmeans_10_result_tbl <-  read_rds("00_Data/data_engineered/code_bd_kmeans_10_result_tbl.rds")

cleaned_retail_tbl <- read_rds("00_Data/cleaned_retail_tbl.rds")
```

## Train/Val/Test
```{r}
time_split_train <- read_rds("00_Data/data_split/time_split_train.rds")
time_split_validation <- read_rds("00_Data/data_split/time_split_validation.rds")
time_split_test <- read_rds("00_Data/data_split/time_split_test.rds")
```


## Functions 
```{r}
source("00_Functions/Visualisation_function/visual.R")
source("00_Functions/Iterative_analysis/product_disctionary.R")
```


```{r}
product_clutser_tbl <- code_bd_kmeans_10_result_tbl

train_X_tbl <- time_split_train$train
val_X_tbl <- time_split_validation$train
test_X_tbl <- time_split_test$train
```


## 3 Join Product Cluster Table with Training Data 
-- 13% of product is NA_Catagory Product: Product with low matching descriptive Information 


```{r}
analysed_data <- train_X_tbl
```


```{r}
cust_product_cluster_tbl <- analysed_data %>% 
    left_join(
        product_cluster_tbl %>% 
            group_by(stock_code) %>% 
            slice(1) %>% 
            ungroup(),
        by = "stock_code"
    ) %>% 
    select(customer_id, invoice_id, invoice_date, stock_code, description, .cluster, stock_price, country, cancellation)
```

## 4 Holiday Feature Engineering 

### 4.1 Format Holiday Data  & Merge 

__Problem:__
Noticed most of the holiday dates are missing from the original retail data 

__Solution:__
fill missing holiday label 
-- label "upwards" & boundary set to within the single month

```{r}
cust_product_cluster_holiday_tbl  <- cust_product_cluster_tbl %>% 
  full_join(
    country_holiday_tbl %>% select(-year, -country_abbr),
    by = c("country"      = "country",
           "invoice_date" = "ds")
    ) %>% 
  mutate(week_date = floor_date(invoice_date, "week")) %>% 
  group_by(week_date, country) %>% 
  fill(holiday, .direction = c("up")) %>% 
  ungroup() %>% 
  select(-week_date) %>% 
  # Removes NA filled rows (missing holiday dates)
  filter(!is.na(customer_id)) %>% 
  mutate(holiday_week = case_when(is.na(holiday) ~ FALSE,
                             TRUE ~ TRUE)) 

cust_holiday_freq_tbl <- cust_product_cluster_holiday_tbl %>% 
    distinct(customer_id, invoice_date, holiday_week) %>% 
    group_by(customer_id, invoice_date) %>% 
    summarise(
        holiday_week_pur  = sum(holiday_week),
        ) %>% 
    ungroup() %>% 
    
    # Aggregate by Customer ID
    group_by(customer_id) %>% 
    summarise(
        .groups           = "drop",
        holiday_week_freq = sum(holiday_week_pur)/n_distinct(invoice_date)
    ) 
    
```

### Characterise Spend Habits

```{r}
customer_spend_habits <- cust_product_cluster_tbl %>% 
    group_by(customer_id, invoice_id) %>% 
    summarise(order_value = sum(stock_price)) %>% 
    ungroup() %>% 
    
    # Aggregate by Customer ID
    group_by(customer_id) %>% 
    summarise(
        frequency     = n(),
        min_spend     = min(order_value),
        median_spend  = median(order_value),
        max_spend     = max(order_value),
        monetary      = sum(order_value),
    ) %>% 
    ungroup()


customer_spend_habits %>% glimpse()
```



## Characterise Product Categories
-- How individual customers have spend purchaing product category in proportions. 
```{r}
customer_product_habits_tbl <- cust_product_cluster_tbl %>% 
    select(customer_id, stock_price, .cluster) %>% 
    group_by(customer_id, .cluster) %>% 
    summarise(stock_price = sum(stock_price)) %>% 
    mutate(prop = stock_price/sum(stock_price)) %>% 
    ungroup() %>% 
    select(-stock_price) %>% 
    pivot_wider(names_from = .cluster,
                values_from = prop,
                values_fill = list(prop = 0),
                names_prefix = "p.cat_")

customer_product_habits_tbl %>% glimpse()
```

```{r}
customer_calender.Month_performance_tbl <- cust_product_cluster_tbl %>%
    mutate(month = lubridate::month(invoice_date, abbr = TRUE)) %>% 
    select(customer_id, stock_price, month) %>% 
    group_by(customer_id, month) %>% 
    summarise(stock_price = sum(stock_price)) %>% 
    mutate(prop = stock_price/sum(stock_price)) %>% 
    ungroup() %>% 
    select(-stock_price) %>% 
    pivot_wider(names_from = month,
                values_from = prop,
                values_fill = list(prop = 0),
                names_prefix = "cal.month_") 

customer_calender.Month_performance_tbl %>% glimpse()
```


```{r}
source("00_Functions/Iterative_analysis/data_partition_time_span_filter.R")

train_cust_id <- cust_product_cluster_tbl %>% 
    distinct(customer_id) %>% pull()

TS_filter_cust_cancel_tbl <- cleaned_retail_tbl %>% 
    filter(cancellation == TRUE) %>% 
    filter_by_cohort_span() %>% 
    filter(customer_id %in% train_cust_id) %>% 
    mutate(stock_price = quantity*unit_price) %>% 
    split_by_time(.assess_days = "90")
```

```{r}
cancellation_product_cluster_tbl <- TS_filter_cust_cancel_tbl$train %>% 
    left_join(
        product_cluster_tbl %>% 
            group_by(stock_code) %>% 
            slice(1) %>% 
            ungroup()
    ) 

customer_refund_freq_behviour_tbl <- cancellation_product_cluster_tbl %>% 
    group_by(customer_id, invoice_id) %>% 
    summarise(order_value = sum(stock_price)) %>% 
    ungroup() %>% 
    group_by(customer_id) %>% 
    summarise(
        refund_frequency = n(),
        tot_refund_value = sum(order_value)
    ) %>% 
    ungroup()

customer_refund_product_freq_behviour_tbl <- cancellation_product_cluster_tbl %>% 
    select(customer_id, stock_price, .cluster) %>% 
    left_join(customer_refund_freq_behviour_tbl) %>% 
    group_by(customer_id, .cluster) %>% 
    summarise(frequency = sum(refund_frequency)) %>% 
    mutate(prop = frequency/sum(frequency)) %>% 
    ungroup() %>% 
    select(-frequency) %>% 
    pivot_wider(names_from = .cluster,
                values_from = prop,
                values_fill = list(prop = 0),
                names_prefix = "refund.cat_")
    
```


## Characterise Recency in Purchase 

```{r}
analyse_date <- max(cust_product_cluster_tbl$invoice_date) +1

customer_recency_habits_tbl <- cust_product_cluster_tbl %>% 
    count(customer_id, invoice_date) %>% 
    group_by(customer_id) %>% 
    summarise(
        first_pur = (analyse_date -(min(invoice_date)))/ddays(1),
        recency  = (analyse_date -(max(invoice_date)))/ddays(1)
    )
```


## Combine All Customer Table

```{r}
customer_trans_habits_joined_tbl <- cust_product_cluster_tbl %>% 
    distinct(customer_id, country) %>% 
    left_join(customer_spend_habits) %>% 
    left_join(customer_recency_habits_tbl) %>% 
    left_join(customer_product_habits_tbl) %>% 
    left_join(customer_calender.Month_performance_tbl) %>% 
    left_join(customer_refund_freq_behviour_tbl) %>% 
    left_join(customer_refund_product_freq_behviour_tbl) %>% 
    left_join(cust_holiday_freq_tbl) %>% 
    mutate(tot_refund_value = -tot_refund_value) %>% 
    mutate_all(~replace_na(., 0))

customer_trans_habits_joined_tbl %>% glimpse()

```


## Collect Feature Engineered Output 
```{r}
engineered_tbl <- customer_trans_habits_joined_tbl
```

```{r}
train_engineered_tbl <- engineered_tbl
```


```{r}
train_engineered_tbl <- read_rds("00_Data/data_engineered/train_engineered_tbl.rds")

validation_engineered_tbl <- read_rds("00_Data/data_engineered/validation_engineered_tbl.rds")

c <- read_rds("00_Data/data_engineered/test_engineered_tbl.rds")
```


```{r}
time_split_train <- read_rds("00_Data/data_split/time_split_train.rds")

time_split_Validation <- read_rds("00_Data/data_split/time_split_Validation.rds")

time_split_test <- read_rds("00_Data/data_split/time_split_test.rds")
```


```{r}
analyse_data <- time_split_test$train
label_data   <- time_split_test$test

engineered_data <- test_engineered_tbl
```



```{r}
cohort_tbl <- analyse_data %>% 
    group_by(customer_id) %>% 
    mutate(
        cohort_date = floor_date(min(invoice_date), "month"),
        cohort      = cohort_date %>% format("%Y%m")
        ) %>% 
    ungroup()

cohort_behaviour_tbl <- cohort_tbl %>% 
    group_by(cohort, customer_id) %>% 
    summarise(
        .groups = "drop",
        n_items   = n(),
        monetary  = sum(quantity),
        frequency = n_distinct(invoice_id)
        ) %>% 
    mutate(
        cohort.items_prop = n_items/sum(n_items),
        cohort.monetary_prop = n_items/sum(monetary),
        cohort.frequency_prop = n_items/sum(frequency)
        ) %>% ungroup()  %>% 
    select(-n_items, -monetary, -frequency)

cohort_behaviour_tbl %>% glimpse()
```


```{r}
customer_joined_tbl <- cohort_behaviour_tbl %>% 
    left_join(engineered_data) %>% 
    left_join(label_data) %>% 
    select(spend_90_total, spend_90_flag, customer_id,
           contains("cohort"),
           contains("holiday"), everything()) %>% 
    # mutate(spend_90_total = log(spend_90_total)) %>% 
    replace_na(
        replace = list(
        spend_90_total = 0,
        spend_90_flag  = 0)
        ) %>% 
    mutate(
        cohort = cohort %>% as.factor(),
        country = country %>% as.factor(),
        spend_90_flag = spend_90_flag %>% as.factor()
        ) 

customer_joined_tbl %>% glimpse()
```

-- No Data Missingness 
```{r}
get_missingness <- function(data){
    data %>% 
    map_df(~sum(is.na(.)/length(.))) %>% 
    gather(key = feature, value = missingness) %>% 
    arrange(desc(missingness))
}

customer_joined_tbl %>% get_missingness()
```


```{r}
test_joined_tbl <- customer_joined_tbl
```


## Save Ready to Model Data  

```{r}
write_rds(test_joined_tbl, "00_Data/data_engineered/90_days_prediction/test_joined_tbl.rds")
```


