---
title: "Static Customer Segmentation"
author: "Seung Hyun Sung"
date: "2/4/2022"
output: 
    html_document:
        theme: flatly
        toc: true
        toc_depth: 2
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
    echo = TRUE,
    message = FALSE,
    warning = FALSE)
```


```{r libraries}
# libraries
library(knitr)
library(timetk)
library(tidytext)
library(plotly)
library(ggwordcloud)
library(ggiraphExtra)
library(fs)
library(readr)
library(tidyverse)
library(tidymodels)
library(tidyquant)
library(recipes)
library(umap)
# Python integration 
library(reticulate)
```


# 1. Set Up 
-- Data 
-- Train/Val/Test
-- Functions 
-- Plan 


## Data 
```{r}
trans_invoice_tbl <- read_rds("00_Data/data_wranggled/trans_data/trans_invoice_tbl.rds")

retail_order_tbl <-  read_rds("00_Data/data_wranggled/trans_data/retail_order_tbl.rds")

products_manual_tbl <-  read_rds("00_Data/data_wranggled/product_data/products_manual_tbl.rds")

code_bd_kmeans_10_result_tbl <-  read_rds("00_Data/data_engineered/code_bd_kmeans_10_result_tbl.rds")

cleaned_retail_tbl <- read_rds("00_Data/cleaned_retail_tbl.rds")
```

## Train/Val/Test
```{r}
time_split_train <- read_rds("00_Data/data_split/time_split_train.rds")
time_split_validation <- read_rds("00_Data/data_split/time_split_validation.rds")
time_split_test <- read_rds("00_Data/data_split/time_split_test.rds")
```


## Functions 
```{r}
source("00_Functions/Visualisation_function/visual.R")
source("00_Functions/Iterative_analysis/product_disctionary.R")
source("00_Functions/Visualisation_function/optimal_kmeans_skree_plot.R")
```


```{r}
product_clutser_tbl <- code_bd_kmeans_10_result_tbl

train_X_tbl <- time_split_train$train
val_X_tbl <- time_split_validation$train
test_X_tbl <- time_split_test$train
```


# 2. Customer (Unsupervised) Segmentation - Static (Time Independent) 

__Objectives:__ 
- Learn & understand customers with similar purchasing behaviour

- Identify relevant (strong correlated) purchasing behaviour feature for the predictive modelling (90-days window CLV)

<!-- __Hypothesis:__ -->
<!-- - Similar Products Embeds Similar Word Token -->
<!-- - Similar Products Have Similar Price Variations -->
<!-- - Similar Products Have Similar Stock Codes (digits) -->

<!-- __Algorithm:__ -->
<!-- - Kmeans: Distance-Based Metric Learning -->
<!-- - DBSCAN:  Density-Based Metric Learning -->


__Problems:__
- The only demographical feature for customer is country 

- Need for information to learn which customers are similar in purchasing behaviour 

__Solution:__
- Implement Product Clustered Feature + Abstract Product Engineered Features to compare customer purchasing preferences on its product level

- Implement Order Cancellation Feature

- (consideration) Implement Holidays Feature: 

-- B2C: Despite the data is mainly B2B retailers it may be possible to distinguish B2C customers by measuring the closness to the holiday dats (Christmas, New years, Easter etc) -> Cross-sell, Gift-Box Strategy Source

-- B2B: By performing time-series forecasting, it might be possible to project how early the product-clustered customeer group stock there ware-house. Potential Risk Hedging + Demand Forecasting Control can be thought here (Not the area of current business objective)



## Data Pre-processing 

```{r}

recipe_spec_customers <- recipe(~., data = customer_trans_habits_joined_tbl) %>% 
    step_rm(customer_id, contains("cal.")) %>% 
    step_nzv(all_predictors()) %>% 
    step_log(all_predictors(), -contains("cat_"), offset = 1) %>% 
    step_range(all_predictors(), -contains("cat_")) %>% 
    prep() 

recipe_spec_customers %>% juice() %>% glimpse()
    
```


# Customer Clustering 
Set Up
-- Train Data Setup
-- Source Kmeans Function 

```{r}
X_train <- recipe_spec_customers %>% juice() 
X_label <- customer_trans_habits_joined_tbl %>% select(customer_id)
```


```{r}
kmeans_mapper <- function(center = 3) {
    set.seed(41)
    X_train %>%
        kmeans(centers = center, nstart = 20)
}

centers_tbl <- tibble(centers = 1:10)

k_means_mapped_tbl <- centers_tbl %>% 
    mutate(k_means = centers %>% map(kmeans_mapper),
           glance = k_means %>% map(broom::glance))
```


### Parameter Selection: Number of K-clustering Selection 
-- k = 5 centers 
```{r}
k_means_mapped_tbl %>% plot_kmeans_scree()
```

### Visualisation 
-- 2D-UMAP
```{r}
umap_results <- X_train %>% 
    umap()

umap_results_tbl <- umap_results$layout %>% 
    as_tibble() %>% 
    setNames(c("V.P1", "V.P2")) %>% 
    cbind(X_train)
```


```{r}
k_means_obj <- k_means_mapped_tbl %>% 
    filter(centers == 5) %>% 
    pull(k_means) %>%  pluck(1)

umap_kmeans_results_tbl <- k_means_obj %>% 
    broom::augment(X_train) %>% 
    bind_cols(X_label) %>% 
    select(customer_id, .cluster) %>% 
    bind_cols(umap_results_tbl)

umap_kmeans_results_tbl %>% 
    ggplot(aes(V.P1, V.P2, colour = .cluster)) +
    geom_point(alpha = 0.5) +
    theme_tq() +
    scale_colour_tq()
```


```{r}
customer_morphology_kmeans_result_tbl <- umap_kmeans_results_tbl
```


```{r}
summary_customer_morphology_tbl <- customer_morphology_kmeans_result_tbl %>% 
    group_by(.cluster) %>% 
    summarise_at(vars(frequency:refund.cat_8), .funs = mean)
```


```{r}
summary_customer_morphology_tbl %>% 
    select(
        # Label 
        .cluster,
        # Customer Purchase Behaviour [RFM] components 
        frequency, median, monetary, first_pur, last_pur,
        # 
        contains("cat_"), contains("refund_")
        ) %>% 
    plot_facet_radar(colour = .cluster,
                     .facet_vars = .cluster)
```




### Intuitive Planning 
-- What are their Strength and the Weakness?
-- How they purchase behaviour varies over time?
-- Are these clustered customers with behaviour the same in the future?
-- Can we predict their future purchasing behaviour?
-- How their purchasing behaviour affect the business and what are the criteria quantifiable. 
-- What are any niche -?
-- What could be potential customer experience scenario? 



### Findings:
--Products 
* Strong corrleation of P.Cat_5, P.Cat_2, median monetary value -> 
* 
```{r}
customer_habit_morphology_tbl <- transcation_product_cluster_tbl %>% 
    left_join(
        customer_morphology_kmeans_result_tbl %>% 
            select(customer_id, .cluster) %>% 
            rename(cust_pp_clutser = .cluster),
        by = "customer_id") %>% 
    select(customer_id, cust_pp_clutser, everything()) 

customer_habit_morphology_tbl %>% glimpse()

```


```{r}
retention_predict_train_tbl <- customer_trans_habits_joined_tbl %>% 
    left_join(
        customer_morphology_kmeans_result_tbl %>% 
            rename(cust.cluster = .cluster) %>% 
            select(customer_id, cust.cluster),
        by = "customer_id") 
    
```


## Save 

```{r}
write_rds(customer_morphology_kmeans_result_tbl, "00_Data/data_wranggled/cluster_data/customer_morphology_kmeans_result_tbl.rds")

write_rds(customer_habit_morphology_tbl, "00_Data/data_wranggled/cluster_data/customer_habit_morphology_tbl.rds")

write_rds(retention_predict_train_tbl, "00_Data/data_engineered/retention_predict_train_tbl.rds")


```


